A new type of automated prover based on category theory

### 2022-08-09 paper.tex
fix NEYC word

\begin{center}
Northern Eastern Yucai School, Shenyang, Liaoning, P.R.China
\end{center}

@@

\section*{Acknowledgments}
I express my sincerest greatest gratitude to my tutor Prof. Shao Xinhui, the Yingcai Project of P.R.China, which enables senior high school students to conduct science research, my senior high academy Northern Eastern Yucai School (NEYC) of P.R.China and the corresponding university Northern Eastern University (NEU) of P.R.China. I also thank my parents for encouraging me to conduct this research project.

>>>>

\begin{center}
Northeast Yucai School, Shenyang, Liaoning, P.R.China
\end{center}

@@

\section*{Acknowledgments}
I express my sincerest greatest gratitude to my tutor Prof. Shao Xinhui, the Yingcai Project of P.R.China, which enables senior high school students to conduct science research, my senior high academy Northeast Yucai School (NEYC) of P.R.China and the corresponding university Northern Eastern University (NEU) of P.R.China. I also thank my parents for encouraging me to conduct this research project.
